---
title: "Diabetes"
author: "SuA"
date: "2022-08-08"
output: html_document
---


## 데이터 불러오기

```{r}
df<-read.csv('./diabetes/diabetes.csv')
str(df)
```

# 변수 설명
- Pregnancies : Number of times pregnant (임신한 횟수)
- Glucose : Plasma glucose concentration a 2 hours in an oral glucose tolerance test
	  (경구 포도당 내성 시험에서 2시간마다 혈장 포도당 농도)
- BloodPressure : Diastolic blood pressure (mm Hg)
	           (확장기 혈압)
- SkinThickness : Triceps skin fold thickness (mm)
	           (삼두근 피부 주름 두께)
- Insulin : 2-Hour serum insulin (mu U/ml)
	 (2시간마다 혈청 인슐린)
- BMI : Body mass index (weight in kg/(height in m)^2)
          (체질량지수)
- DiabetesPedigreeFunction : Diabetes pedigree function
			 (당뇨병 유전)
- Age : Age (years)
          (나이)
- Outcome : Class variable (0 or 1) 268 of 768 are 1, the others are 0
	    (당뇨냐 아니냐)

```{r}
head(df)
```

```{r}
summary(df)
```
17번이나 임신한 사람이 있음 -> 이상치일까?
glucose 최솟값이 0임 -> 이상치일까?

```{r}
sum(df$BloodPressure==0)
```

```{r}
boxplot(df$BloodPressure)
```
```{r}
boxplot(df$Glucose)
```

```{r}
sum(df$Glucose==0)
sum(df$BloodPressure==0)
sum(df$SkinThickness==0)
sum(df$Insulin==0)
sum(df$BMI==0)
sum(df$DiabetesPedigreeFunction==0)
```

df[which(df$Glucose==0),]$Glucose<-NA


```{r}
remove_zero<-function (col) {
    cat(col)
    #cat(df[, col])
    cat(df[df[, col]==0, col])
    #df[df[, col]==0, col] <-NA
}
```


```{r}
remove_zero('Insulin')
```


```{r}
df$Insulin
```


```{r}
sapply('Insulin', remove_zero)
```


```{r}
sum(is.na(df$Insulin))
```


```{r}
sum(df$Insulin==0)
```

```{r}
df$Glucose
```


```{r}
df[df[, 'Glucose']==0, 'Glucose'] <-NA
```


```{r}
sum(is.na(df$Glucose))
```


```{r}
df[which(df$Glucose==0),]$Glucose<-NA
```

